Naturalness in U(1) extensions of the MSSM

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Added some more discussion of the chargino limits.

%   For this we also fix [what we fix + explain different choices to
%   before and their impact].
\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{all_models_tuning_vs_higgs.png}}
\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
  MSSM (green), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue) and
  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red).}
\label{Fig:e6ssmvsmssm}
\end{center}
\end{figure}
In Fig \ref{Fig:e6ssmvsmssm} we see that as expected the minimum
tuning in the model for the E$_6$SSM is increased by the mass of the
$Z^\prime$ boson.  Since with such a low cutoff the stop masses have
little impact on the tuning, the tuning here also does not depend much
on the Higgs mass.  However the tuning from the $Z^\prime$ mass
appears already at tree level and is unavoidable regardless of the
cutoff scale chosen.

Therefore the tuning in these models depends on less assumptions than
the tuning which concerns people in the MSSM and the lowest tuned
models are adderessed directly with $Z^\prime$ searches.

In the MSSM the tuning can also be attcked more directly by looking at
chargino mass limikts as this rasies $\mu$ directly.  [Stuff about
  chargino limits, then show plots in MSSM and E6SSM]
%    - plots of chargino bound impacts

>>>>

%   For this we also fix [what we fix + explain different choices to
%   before and their impact].
\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{all_models_tuning_vs_higgs.png}}
\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
  MSSM (green), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue) and
  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red).}
\label{Fig:e6ssmvsmssm}
\end{center}
\end{figure}
In Fig \ref{Fig:e6ssmvsmssm} results from the scan are plotted showing
the tuning for each case against the lightest Higgs mass.  As expected
the dependence on the Higgs mass is now quite weak, while the minimum
tuning in the model for the E$_6$SSM is increased by the mass of the
$Z^\prime$ boson.  So in the case of a very low cutoff much of the
tuning required to get a 125 GeV Higgs has gone away.  However the
tuning from the $Z^\prime$ mass appears already at tree level and is
unavoidable regardless of the cutoff scale chosen, so in the E$_6$SSM
current limits on the mass of the $Z^\prime$ boson imply that the
E$_6$SSM fine tuning must be at least 100 regardless of assumptions
about the way SUSY breaking happens.  Additionally if run II of the
LHC pushes the limit on the $Z^\prime$ mass to be above $4.5$ TeV then
the fine tuning in the model will be greater than at least 350.

This demopnstrates two important points about these $U(1)$
extensions. Firstly that limits on the $Z^\prime$ mass play an
incredibly important role in constraining natural scenarios in such
models and secondly that the tuning from the $Z^\prime$ limits in
these models depends on less assumptions about SUSY breaking than the
tuning reqyired by the $125$ GeV Higgs measurement which concerns
people in the MSSM.

However we should also acknowledge that there are other limits which
play a similar role.  Chargino limits directly constrain the $\mu$
parameter (or effective $\mu$ parameter in these $U(1)$ extensions).
Unfortunately the chargino limits from the LHC are not general enough
so as to provide an absolute constraint on the model [Add: XSdetails on
  limits and what they depend on].

Nonetheless the MSSM the impact of chargino limit is shown in
Fig. \cite{}.  There we see that if the the full parameter space with
$m_{\chi^\pm} < 700$ GeV was excluded the impact would be to make the
tuning in the MSSM with a $20$ TeV cuttoff slightly worse than that of
the E$_6$SSM with the same cuttoff and a $Z^\prime$ mass just larger
than current limits.  would be similar to that can also be attcked
more directly by looking at chargino mass limits as this rasies $\mu$
directly.  In the E$_6$SSM, while raising the chargino limit can have
the same impact in princuiple, due to current limits on the $Z^\prime$
mass already imposing a significant degree of tuning, chargino masses
do not make much of a noticable change.

[show plots in MSSM and E6SSM if it gets clened up, though maybe we
  can just leave it out if it only shows that there is no big impact?]
%    - plots of chargino bound impacts
